Supplementary Materials

### 2018-11-24 paper/supp.tex
Updated paper with clustering results on S1

\section{Cluster Analysis}
We now present the full description of where each point is in each clustering algorithm. The explanation in the paper supplements this well enough to clearly understand the segregation of points by both algorithms.\\

\includegraphics[scale=0.65]{clustering.png}
\begingroup
\captionof{figure}{Clustering by DBSCAN and Mean-Shift algorithms on the subset of the data}
\endgroup

>>>>

\section{Cluster Analysis}
We now present the full description of where each point is in each clustering algorithm. The explanation in the paper supplements this well enough to clearly understand the segregation of points by both algorithms.

\subsection{Analysis on $S_1$}
Figure 17 shows the analysis for $S_1$. The Silhouette score for DBSCAN here was 0.635.

We make the following observations. The largest clusters for both the algorithms are very similar \textbf{(row 9)}. The two points in the MS cluster that were not in DBSCAN's largest cluster were in its second largest cluster \textbf{(row 2)}. All the clusters of the mean-shift algorithm that were of size 4 or less were marked as individual clusters by DBSCAN \textbf{(rows 5-8 and row 1)}. More surprisingly, the cluster of 19 points identified by mean-shift was marked as 19 individual clusters by DBSCAN \textbf{(row 4)}. Finally, a considerable part of mean-shift's second-largest cluster was also identified as individual points by DBSCAN \textbf{(row 3)}.

\includegraphics[scale=0.65]{cluster_s1.png}
\begingroup
\captionof{figure}{Clustering by DBSCAN and Mean-Shift algorithms on $S_1$}
\endgroup

\subsection{Analysis on $S_2$}
Figure 18 shows the analysis for $S_2$. As noted in the paper, the Silhouette score for DBSCAN for this subset was 0.571. \\

\includegraphics[scale=0.65]{clustering.png}
\begingroup
\captionof{figure}{Clustering by DBSCAN and Mean-Shift algorithms on $S_2$}
\endgroup
